Response to reviewers and editorial comments for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2023-01-17 src/docs_paper/paper.Rmd
Spatial effects clarification and response, Sobol calculation and no interactions response, FSW limiation, Figure 1 response

We considered four model specifications for the space-age-time multinomial model for the three risk groups (Supplementary Appendix A.1.2).
All models included intercepts for each risk group, as well as age, country, and age-country random effects.
We used spatial effects to allow variation in risk group proportions by district, and considered alternative model specifications with either independent spatial effects or spatially correlated effects which share information more between neighboring districts than those far apart.
Similary, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent temporal effects versus first-order auto-regressive temporal effects where a smooth temporal trend is assumed. 
<!-- Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts. -->
To understand the importance of each part of the model we analysed the relative sizes of the variance parameters for each effect.

For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Supplementary Appendix A.1.3).
Each included an intercept, age and country effects, and a spatial effect allowing district-level variation.
Both independent and spatially correlated spatial effects were considered.
To improve estimation with sparse data, during model selection we considered alternatives with national-level covariates for either the proportion of men who reported ever having paid for sex or having paid for sex in the last twelve months [@hodgins2022population].

@@

The best fitting multinomial regression model included correlated spatial effects and independent and identically distributed temporal effects.
<!-- but not spatio-temporal interactions. -->
The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
Model performance according to the CPO criterion is provided in Supplementary Appendix A.1 for all models we considered.
Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Supplementary Fig B.5 - B.17).

>>>>

We considered four model specifications for the space-age-time multinomial model for the three risk groups (Supplementary Appendix A.1.2).
All models included intercepts for each risk group, as well as age, country, and age-country random effects.
To account for district-level variation we used spatial random effects consisting of a parameter for each district. 
We considered alternative model specifications in which the spatial random effects were either independent or spatially correlated such that more information was shared between neighboring districts than those far apart.
Similarly, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent versus first-order auto-regressive where a smooth temporal trend is assumed. 
<!-- Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts. -->
To understand the importance of each part of the model we analysed the relative sizes of the variance parameters for each effect.

For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Supplementary Appendix A.1.3).
Each included an intercept, age and country random effects, and a spatial random effect allowing district-level variation.
Both independent and spatially correlated spatial random effects were considered.
To improve estimation with sparse data, during model selection we considered alternatives with national-level covariates for either the proportion of men who reported ever having paid for sex or having paid for sex in the last twelve months [@hodgins2022population].

@@

The best fitting multinomial regression model included correlated spatial random effects and independent and identically distributed temporal random effects.
<!-- but not spatio-temporal interactions. -->
The best logistic regression model for transactional sex included correlated spatial random effects and the proportion of men who reported ever paying for sex covariate.
Model performance according to the CPO criterion is provided in Supplementary Appendix A.1 for all models we considered.
Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Supplementary Fig B.5 - B.17).

### 2023-01-17 src/docs_review/review.Rmd
Spatial effects clarification and response, Sobol calculation and no interactions response, FSW limiation, Figure 1 response

Using district-level spatial random effects allowed us to account for subnational variation in risk group proportions.
We considered both spatially unstructured (IID) and spatially structured (Besag) random effects, which can be implemented in `R-INLA` by setting `model = "iid"` or `model = "besag"` respectively.

@@

```{r}
#' TODO Calculate the average Sobol index for survey random effects
sobol <- 1
```

Fitting each country individually, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects was on average `r sobol`/% (Supplementary Figure B.3).
This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).

We had wanted to include the spatiotemporal interaction terms regardless, first for statistical completeness, and second to demonstrate how complex three-way^[As all random effects in the model are interacted with category.] interactions can be specified in `R-INLA` by careful use of the `group` and `replicate` options.
However, we found that including these terms substantially increased the computational burden of the model when fitting all countries jointly, so in the end decided to exclude them.

@@

Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
We have noted this in the limitations section of the discussion.

@@

Table B.3 in the appendix provides an alternative tabulation of the surveys we used, with sample size further broken down by age group.
We are unsure on how to make Figure 1 might clearer.
Other examples of similar figures in published papers include @giguere2021trends (Figure 1), ...

>>>>

We did not use the specific term "sub-national effect" in the manuscript.
We believe the reviewer is referring to the term "spatial effect", which we use to describe district-specific effects that allow the model to capture district-level variation in risk group proportions, primarily informed by survey data in each district.

Thank you to the reviewer for highlighting the omission of specific definition for this term.
Throughout the manuscript, we have replaced references to "effect" by the more accurate "random effect", and have clarified the usage of spatial random effect where it first appears in the methods section as follows:

> All models included intercepts for each risk group, as well as age, country, and age-country random effects. To account for district-level variation we used spatial random effects consisting of a parameter for each district. We considered alternative model specifications in which the spatial random effects were either independent or spatially correlated such that more information was shared between neighboring districts than those far apart. Similarly, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent versus first-order auto-regressive where a smooth temporal trend is assumed.

@@

```{r}
df <- read_csv("depends/aaa-variance-proportions.csv")
sobol <- 100 * mean(df$percentage_variance_sur_idx, na.rm = TRUE)
```

We share the reviewer's interest in the spatiotemporal interaction in risk group proportions, which would allow variation in temporal trend by country.
However, we found that these interactions made the model computationally intractable to estimate given the large number of districts, years, age groups and risk groups involved.
This is a limitation of our analysis, but, in practice, we do not believe this has a large impact on our results because overall we found that risk group proportions were very stable over time, while they varied substantially spatially.
More specifically, when we fit the model to each country individually, which can be considered as an extreme version of country-specific spatiotemporal interactions, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects^[For those countries where such a random effect could be meaningfully defined.] was on average `r sobol`/% (Supplementary Figure B.3).
This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).

@@

Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
We have noted this in the limitations section of the discussion:

> We have the least confidence in our estimates for the FSW risk group. As well as having the smallest sample sizes, our transactional sex estimates do not overcome the difficulties of sampling hard to reach groups. We inherent any limitations of the national FSW estimates which we adjust our estimates of transactional sex to match. Furthermore, we do not consider seasonal migration patterns, which may particularly affect FSW size.

@@

In our and other previous work, figures similar to Figure 1 have been effective at concisely visualising inclusion of a large number of surveys across several countries and types (see, for example, Figure 1 of @giguere2021trends), and we prefer to retain this figure.
Supplementary Table B.3 provides an alternative tabular summary of the surveys analysed, with sample size broken down by age group. 
We have extended the caption of Figure 1 to draw attention to this alternative presentation:

> **Fig 1.** Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. Details of included surveys are in Supplementary Table B.3.
